\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-10 chapters/supplementary.tex
Minor update supplementary

@@

\subsection{MWS on SSBM graphs}

\begin{prop}\label{prop:MWS_SSBM_1}
Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$. Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found. Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters. 
\end{prop}

\begin{prop}\label{prop:MWS_SSBM_2}
Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
\begin{equation}
\sum_{ij} \frac{|E_ij^+|}{||}
\end{equation}
\end{prop}

Then, the MWS algorithm will assign highest priority to 
Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm

\begin{itemize}
\item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
\item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
\end{itemize}
will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e. $S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e. $S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
\TODO{Assumption about $\sigma$?}

>>>>

\subsection{Mutex Watershed on SSBM graphs}
\TODO{}

% \begin{prop}\label{prop:MWS_SSBM_1}
% Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$. Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found. Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters. 
% \end{prop}

% \begin{prop}\label{prop:MWS_SSBM_2}
% Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
% \begin{equation}
% \sum_{ij} \frac{|E_ij^+|}{||}
% \end{equation}
% \end{prop}

% Then, the MWS algorithm will assign highest priority to 
% Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm

% \begin{itemize}
% \item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
% \item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
% \end{itemize}
% will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
% Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e. $S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e. $S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
% \TODO{Assumption about $\sigma$?}

@@
